Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-12 RNARedPrint.tex

By this choice of $\F$, the sum $\sum_{f\in\F} f(S)$ (for any $S\in\Sigma^n$) corresponds to the energy in
Eq.~$(\ref{eq:mainproblem}),$ using the equivalence of Eq.~(\ref{eq:feature-energy-transformation}). 
Consequently, the network encodes the partition function $\partfun{\pi_0,\dots,\pi_k}$ of Eq.~(\ref{eq:mainproblem}). Subsequently, we show how to efficiently compute this partition function based on the network.

>>>>

By these definitions, the network encodes the partition function $\partfun{\pi_0,\dots,\pi_k}$ of Eq.~(\ref{eq:mainproblem}); also confer Eq.~(\ref{eq:feature-energy-transformation}). Subsequently, we show how to efficiently compute this partition function based on the network.
